---
title: "README"
author: "lee"
date: "2/6/2021"
output: html_document
---

# Modify your variable before running 

# define where the files are! change "dataDir" to you dir for data to run 

dataDir -- where the downloaded dir is extracted

    Default: dataDir ="UCI HAR Dataset/"

tidyData -- tidy data site stored file name 
    
    Default: tidyData ="myData.txt"


meanSbjExcData -- where the independent tidy data set is stored

    Default: meanSbjExcData ="meanSbjExcData.txt"

# use fread() for all !!

# Code run through



1. read test data -- X_test.txt, X_train.txt to df-data

```{r}
##Processing the DATA

dt <- data.table()

#read data (you can try 150 roll for a start) 
#dt <- fread(testData, nrows=150)

# read test data, train data in the data table

dt <- fread(testData)
dt <- rbind(dt,fread(trainData))

#read colum names from features.text, set the column names according feature
featureNames <- fread(features)
setnames(dt,as.character(featureNames$V2))

# subset mean std var with regX -- 89 var in total out of 561 (What did you get?)
dt <- dt[, names(dt) %like% "(.*)[Ss]td(.*)|(.*)[mM]ean(.*)", with=F]

```


2. Read the subject ID as a column 

```{r}
## Reading the subject id as column

subjectDt <- fread(testSbj)
subjectDt <- rbind(subjectDt,fread(trainSbj))
setnames(subjectDt,"studysubjects")


```


3. Read Excerise from both test and traning data, merger with the excerise ID <-> Name table. 

```{r}
## Read the Excerises and 

#read test and train data from y_test.txt amd y_train.txt
exeDt <- fread(testExe)
exeDt <- rbind(exeDt,fread(trainExe))


# set the table name to be exerciseid
setnames(exeDt,"execeriseid")

# read in exercise from activity_labels.txt
execerise = paste(dataDir,"activity_labels.txt",sep = "")
exefactorDt <- fread(execerise)
setnames(exefactorDt,"V2", "execerise")
factor(exefactorDt$execerise)


#setkey(exeDt,execeriseid)
#setkey(exefactorDt,V1)
# merge 2 tables without sorting according to execeriseid's index
execerisDT<- merge(exeDt,exefactorDt, by.x = "execeriseid", by.y = "V1",all.x = T, sort = F)

```


4. cbind all together

```{r}
# Cbind all data tables together ,,, not very elegant ..:) does the job

resultDT <-data.table()
resultDT <- cbind(resultDT,subjectDt)
resultDT <- cbind(resultDT,execerisDT)
resultDT <- cbind(resultDT,dt)
fwrite(resultDT,outputFile)
```

5. group/summarize resultDT, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

```{r}
#data set represent average of each variable for each activity and each subject
meanSbjExc<- resultDT %>% group_by(studysubjects,execerise) %>% summarise(across(names(dt),mean,na.rm = TRUE))
# save to text file
fwrite(meanSbjExc,meanSbjExcData)
```
